Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-08-14 journal-draft/ettdoc.tex
C1-4 to C1-10 are done

A distributed clustering scheme ROSS is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 

@@

We give the definition of cluster in CRN as follows. 
A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
A cluster can be formed only by the cluster head.
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The size of $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
The notations used in the system model are listed in Table~\ref{tab1}.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
%$k_i$   & set of available channels at CR node $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the cluster size which is preferred\\
$S_i$ & a set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
$f(C)$ & the number of CCs of a cluster $C$, which is used \\
& in the problem description\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
 $|C_i|$ & size of the cluster $C_i$\\
 $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
\bottomrule
\end{tabular}
\end{table}

@@

\item \textit{Neighborhood connectivity degree} $g_i$: the number of CCs which are available for $i$ and all of its neighbors.
$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which represents the ability of $i$ to form a robust cluster with its neighbors.
\end{itemize}
Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector}.
Figure~\ref{fig1} illustrates an example CRN where every node's connectivity vector is shown.	
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.7\linewidth]{figure1.pdf}
% \includegraphics{figure1.pdf}
	\caption{Connectivity graph of the example CRN and the connectivity vector $(d_i, g_i)$ for each node. The desired cluster size $\delta =3$. The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$. Dashed edge indicates the end nodes are within each other's transmission range.}
	\label{fig1}
\end{figure}

@@

After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster. 
Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree to all of its neighbors. 
%wrong:
%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
%\begin{theorem}{lemma}
%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
%\end{theorem}
%\begin{proof}
%We use contradiction to prove. 
%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
%\end{proof}
When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $M$. 
%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
The manipulation of the individual connectivity degree of the cluster members accelerates the decision on the cluster heads.
%, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
%We have the following theorem to show that when there is no one secondary which shares no CC with any other secondary users, \ie
%all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
We have the following theorem to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
\begin{theorem}
\label{clustering:theorem}
Given a CRN, it takes at most $N$ steps that every secondary user either becomes cluster head, or gets included into at least one cluster.
\end{theorem}
Here, by \textit{step} we mean one secondary user executing Algorithm~\ref{clustering:theorem} for one time.
The Proof is in Appendix~\ref{proof_clustering:theorem}.
%
The procedure of the proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a list as discussed in the example in the proof.
%
If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
As Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
%
%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, then the outcome is shown in Figure~\ref{fig2}.
Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.

@@

Hence, a cluster head excludes some cluster members when the cluster size exceeds $t\cdot \delta$, where constant parameter $t$ is dependent on the network density and CR nodes' transmission range and $t>1$.

@@

The $t$ is set to 1.3.

@@

Now we apply both ROSS-DGA and ROSS-DFA to the toy network in Figure~\ref{fig2} which has been applied the phase I of ROSS.
In the network, node $A$'s claiming clusters are cluster $C(C), C(H)\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
The two possible strategies of node $A$ is illustrated in Figure \ref{fig3}.
In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy shown in \ref{AinH}.
After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.

@@

Simulation consists of two parts, first we investigate the performance of centralized scheme and the distributed schemes in a small network, as there is no polynomial time solution available to solve the centralized problem.
In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
The following simulation setting is the same for both simulation parts.
CRs and PUs are deployed on a two-dimensional Euclidean plane.
%Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
The constant $t$ which is used to control cluster size for ROSS (discussed in Section~\ref{ross_p2_cluster_pruning}) is 1.3.
CR users are assumed to be able to sense the existence of primary users and identify available channels.
All primary and CR users are assumed to be static during the process of clustering.
The simulation is written in C++, and the performance results are averaged over 50 randomly generated topologies, and the confidence interval corresponds to 95\% confidence level.

\subsection{Centralized Schemes vs. Decentralized Schemes}
There are 10 primary users and 20 CR users dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where we set the transmission ranges of primary and CR users to $A/3$.
%There are 10 available channels. 
%With this setting, the average number of neighbours of one CR user is 4.8.
%Each primary user randomly occupies one channel, and 
When clustering scheme is executed, around 7 channels are available on each CR node.
The desired cluster size $\delta$ is 3.
As for the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.

@@

\appendices
\section{Peudo Code for the Algorithm~\ref{alg0}, \ref{alg_size_control_available_CCC} and~\ref{alg4}}
\begin{algorithm}              % enter the algorithm environment
\caption{ROSS phase I: cluster head determination and initial cluster formation for CR node $i$}          % give the algorithm a caption
\label{alg0} 
\DontPrintSemicolon
\SetAlgoLined
\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ means cluster heads. Empty sets $\tau_1,\tau_2$}
\KwResult{Returning 1 means $i$ is cluster head, then $d_j$ is set to 0, $j\in \text{Nb}(i)\setminus \Lambda$. returning 0 means $i$ is not cluster head.}

\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i \geq d_j$}{
	return 1;
	}
\eIf{$\exists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i > d_j$}{
	return 0;}{
	\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_j == d_i$}{
	$\tau_1 \leftarrow j$
	}
}
\If{$\nexists j\in \tau_1$, such that $g_i \leq g_j$}{
	return 1;
	}
\eIf{$\exists j\in \tau_1$, such that $g_i < g_j$}{
	return 0;
	}
	{\If{$\nexists j\in \tau_1$, such that $g_j == g_i$}{
		$\tau_2\leftarrow j$
		}
	}
\If{$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$}{
	return 1;
	}
	{return 0;
	}
\end{algorithm}

>>>>

A distributed clustering scheme ROSS (Robust Spectrum Sharing) is proposed in~\cite{Li11_ROSS} under the game theoretic framework. 

@@

We give the definition of cluster in CRN as follows. 
A cluster $C$ is a set of secondary nodes, and there is one set of common channels which are available for each node.
In particular, a cluster consists of a cluster head $h(C)$ and a number of cluster members, and the cluster head is able to communicate with any cluster member directly.
Our scheme enables the cluster heads are selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The size of $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs in cluster $C$, $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
The notations used in the system model are listed in Table~\ref{tab1}.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
%$k_i$   & set of available channels at CR node $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the cluster size which is preferred\\
$S_i$ & a set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
$f(C)$ & the number of CCs of a cluster $C$, which is used \\
& in the problem description\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
 $|C_i|$ & size of the cluster $C_i$\\
 $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
\bottomrule
\end{tabular}
\end{table}

@@

\item \textit{Neighborhood connectivity degree} $g_i$: the number of CCs which are available for $i$ and all of its neighbors.
$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$, which represents the ability of $i$ to form a robust cluster with its neighbors.
\end{itemize}
Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector}.
Figure~\ref{fig1} illustrates an example CRN where every node's connectivity vector is shown.	
In Figure~\ref{fig1}, some primary users are randomly deployed in the network, and they are free to choose one channel out of the set of licensed channels $\mathcal{K}$ to operate.
As to the secondary users, the channels they are allowed to use are those which are not ruled out by the primary users in their vicinities. 
The sets of the indices of the available channels sensed by each node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$.
%C1-5
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.7\linewidth]{figure1.pdf}
% \includegraphics{figure1.pdf}
	\caption{Connectivity graph of the example CRN and the connectivity vector $(d_i, g_i)$ for each node. Primary users are not shown. The desired cluster size $\delta =3$. Dashed edge indicates the end nodes are within each other's transmission range.}
	\label{fig1}
\end{figure}

@@

After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster. 
Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$, and broadcasts the new individual connectivity degree to all of its neighbors. 
%wrong:
%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
%\begin{theorem}{lemma}
%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
%\end{theorem}
%\begin{proof}
%We use contradiction to prove. 
%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
%\end{proof}
When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications from different cluster heads, $d_i$ is still set to be $M$. 
%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
The manipulation of the individual connectivity degree of the cluster members accelerates the decision on the cluster heads.
%, which enables the nodes which are outside of the cluster can possibly become cluster heads or can also be included into other clusters.
%We have the following theorem to show that when there is no one secondary which shares no CC with any other secondary users, \ie
%all secondary users' individual connectivity degrees are greater than zero, then every secondary user will eventually be either integrated into a certain cluster, or becomes a cluster head.
We have the following theorem to show that every secondary user will eventually be either integrated into a certain cluster or becomes a cluster head.
\begin{theorem}
\label{clustering:theorem}
Given a CRN, it takes at most $N$ steps before every secondary user either becomes cluster head, or gets included into at least one cluster.
\end{theorem}
Here, by \textit{step} we mean Algorithm~\ref{clustering:theorem} is executed by a secondary user for one time.
Note that the minimum number of steps is 1, \eg when a cluster head is elected and all the other nodes are within its neighborhood.
The Proof on the upper bound of the steps is given in Appendix~\ref{proof_clustering:theorem}.
%The proof also illustrates the maximal time needed to conduct Algorithm~\ref{clustering:theorem}. 
Consider an extreme scenario, where all the secondary nodes sequentially execute Algorithm~\ref{alg0}, \ie they constitute a chain as discussed in the example in the proof.
%
Assuming there is a token in the CRN, one node is allowed to execute Algorithm~\ref{alg0} only when it holds the token, and it then transfers the token to the neighboring node on the chain.
If one step can be finished within a certain time span $T$, then the total time needed for the network to conduct Algorithm~\ref{clustering:theorem} is $N*T$.
%C1-6
As Algorithm~\ref{alg0} can be executed concurrently by different secondary users, the needed time can be considerably reduced.
%According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.
%
%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
If we apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}, the outcome is shown in Figure~\ref{fig2}.
Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C(H)$ is $\{H, B, A, G\}$.

@@

Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
We set the threshold as $t\cdot \delta$, where $\delta$ is the desired cluster size.
The constant parameter $t$ is usually larger than 1 and is dependent on the network density and CR nodes' transmission range, in particular, $t$ is between 1 and the ratio between the average number of neighbors and the desired size.
A smaller or bigger $t$ may lead to more clusters with smaller or larger size than $\delta$.
Because of $t$, the threshold is larger than the desired size, then there will be some nodes choosing to affiliate with other clusters in the following phases.
%C1-7

@@

%The $t$ is set to 1.3. 	
%C1-7

@@

Now we apply both ROSS-DGA and ROSS-DFA to the network in Figure~\ref{fig2} which has been applied the phase I of ROSS.
%C1-8
In the network, node $A$'s claiming clusters are cluster $C(C), C(H)\in S_A$, their members are $\{A,B,C,D\}$ and $\{A,B,H,G\}$ respectively. 
The two possible strategies of node $A$ is illustrated in Figure \ref{fig3}.
In Figure \ref{AinC}, node $A$ staying in $C(C)$ and leaving $C(H)$ brings 2 more CCs to $S_A$, which is more than that brought by another strategy shown in \ref{AinH}.
After the decisions made similarly by the other debatable nodes $B$ and $D$, the final clusters are formed as shown in Figure~\ref{final_clustering_ross}.

@@

Simulation consists of two parts, first we investigate the performance of centralized scheme and the distributed schemes in a small network, as there is no polynomial time solution available to solve the centralized problem.
In the second part, we investigate the performance of the proposed distributed schemes in the CRN with different scales and densities.
The following simulation setting is the same for both simulation parts.
CRs and PUs are deployed on a two-dimensional Euclidean plane.
%Complying with the system model, the CR node residing within another CR node's transmission range is seen as neighbour of that CR node.
The number of licensed channels is 10, each PU is operating on each channel with probability of 50\%.
The other parameters \ie the number of CR and PU, and their transmission ranges are given in the beginning of the respective simulation sections.
%C1-10
The constant $t$ which is used to control cluster size for ROSS (discussed in Section~\ref{ross_p2_cluster_pruning}) is 1.3.
CR users are assumed to be able to sense the existence of primary users and identify available channels.
All primary and CR users are assumed to be static during the process of clustering.
The simulation is written in C++, and the performance results are averaged over 50 randomly generated topologies, and the confidence interval corresponds to 95\% confidence level.

\subsection{Centralized Schemes vs. Decentralized Schemes}
In this part of simulation, there are 10 primary users and 20 CR users dropped randomly (with uniform distribution) within a square area of size $A^{2}$, where $A$ is a positive value and we set the transmission ranges of primary and CR users to $A/3$.
%C1-10, C1-9
%There are 10 available channels. 
%With this setting, the average number of neighbours of one CR user is 4.8.
%Each primary user randomly occupies one channel, and 
When clustering scheme is executed, around 7 channels are available on each CR node.
The desired cluster size $\delta$ is 3.
As for the centralized scheme, the parameters used in the \textit{punishment} for choosing the clusters with undesired sizes are set as follows, $\rho_1 =  0.4$, $\rho_2 =  0.6$.

@@

\appendices
\section{Peudo Code for the Algorithm~\ref{alg0}, \ref{alg_size_control_available_CCC} and~\ref{alg4}}
\begin{algorithm}              % enter the algorithm environment
\caption{ROSS phase I: cluster head determination and initial cluster formation for CR node $i$}          % give the algorithm a caption
\label{alg0} 
\DontPrintSemicolon
\SetAlgoLined
\KwIn{$d_j, g_j, j\in \text{Nb}(i)\setminus \Lambda$, $\Lambda$ denotes the set of cluster heads among $\text{Nb}(i)$. Empty sets $\tau_1,\tau_2$}
\KwResult{Returning 1 means $i$ is cluster head, and $d_j$ is set to 0, $j\in \text{Nb}(i)\setminus \Lambda$. Returning 0 means $i$ is not cluster head.}
%C1-6-wording
\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i \geq d_j$}{
	return 1;
	}
\eIf{$\exists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_i > d_j$}{
	return 0;}{
	\If{$\nexists j\in \text{Nb}(i)\setminus \Lambda$, such that $d_j == d_i$}{
	$\tau_1 \leftarrow j$
	}
}
\If{$\nexists j\in \tau_1$, such that $g_i \leq g_j$}{
	return 1;
	}
\eIf{$\exists j\in \tau_1$, such that $g_i < g_j$}{
	return 0;
	}
	{\If{$\nexists j\in \tau_1$, such that $g_j == g_i$}{
		$\tau_2\leftarrow j$
		}
	}
\If{$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$}{
	return 1;
	}
	{return 0;
	}
\end{algorithm}
